### 2013-08-29 Placeholder/thesis/bibliography.tex

\begin{thebibliography}{}

 \bibitem{udp}
  \emph{RFC 768 - User Datagram Protocol};
  tools.ietf.org;
  dostęp: sierpień 2013;
  w: http://tools.ietf.org/html/rfc768

 \bibitem{tcp}
  http://tools.ietf.org/html/rfc793

 \bibitem{http1}
  http://www.w3.org/Protocols/

 \bibitem{http2}
  http://tools.ietf.org/html/rfc2616

 \bibitem{soap}
  http://www.w3.org/TR/soap12-part1/

 \bibitem{rest}
  http://www.ics.uci.edu/~fielding/pubs/dissertation/rest\_arch\_style.htm

 \bibitem{odata}
  http://www.odata.org/

%  \bibitem{des:pat:strategy} Gamma, E., Helm, R., Johnson, R., Vlissides, J.
%                             (2010).
%                             \emph{Wzorce projektowe. Elementy oprogramowania obiektowego wielokrotnego użytku.}
%                             Wydawnictwo HELION.
%                             ISBN 978-83-246-2662-5.
%                             \textbf{321-333}

\end{thebibliography}