### 2013-09-01 Placeholder/thesis/bibliography.tex
Updated work plan

\begin{thebibliography}{}

 \bibitem{graf:przet:obr}
  T. Pavlidis.
  (Warszawa 1987).
  \emph{Grafika i przetwarzanie obrazów: algorytmy.}
  WNT.

 \bibitem{anal:przet:obr}
  Tadeusiewicz R., Korohoda P.
  (Kraków 1997).
  \emph{Komputerowa analiza i przetwarzanie obrazów.}
  Wydawnictwo Fundacji Postępu Telekomunikacji.
  ISBN 83-86476-15-X.

 \bibitem{roz:obr}
  Tadeusiewicz R., Flasiński M.
  (Warszawa 1991).
  \emph{Rozpoznawanie obrazów.}
  PWN.
  ISBN 83-01-10558-5.

 \bibitem{geo:tools}
  Schneider P. J., Eberly D. H.
  (USA 2003).
  \emph{Geometric Tools for Computer Graphics.}
  Morgan Kaufmann Publishers.
  ISBN 1-55860-594-0.

 \bibitem{pic:desc}
  Shaw A. C.
  \emph{A formal picture description scheme as a basis for picture processing systems.}

 \bibitem{img:proc}
  Russ J. C.
  (USA 1998).
  \emph{The Image Processing Handbook.}
  CRC Press.
  ISBN 0849325323.

 \bibitem{now:przet:obr}
  Watkins C. D., Sadun A., Marenka S. R.
  \emph{Nowoczesne metody przetwarzania obrazu.}

 \bibitem{mar:det}
  Hirzer M.
  \emph{Marker Detection for Augmented Reality Applications.}

 \bibitem{udp}
  \emph{RFC 768 - User Datagram Protocol};
  tools.ietf.org;
  dostęp: sierpień 2013;
  w: http://tools.ietf.org/html/rfc768

 \bibitem{tcp}
  http://tools.ietf.org/html/rfc793

 \bibitem{http1}
  http://www.w3.org/Protocols/

 \bibitem{http2}
  http://tools.ietf.org/html/rfc2616

 \bibitem{soap}
  http://www.w3.org/TR/soap12-part1/

 \bibitem{rest}
  http://www.ics.uci.edu/~fielding/pubs/dissertation/rest\_arch\_style.htm

 \bibitem{odata}
  http://www.odata.org/

\end{thebibliography}