### 2014-04-14 Cassandra/thesis/main.tex
Modified document structure, introduced placeholder for history and architecture sections

\documentclass{report}

% language settings %
\usepackage[utf8]{inputenc}
\usepackage[MeX]{polski}

% bibliography with online sources %
\usepackage[backend=bibtex]{biblatex}
\bibliography{references.bib}

% package for generating urls %
\usepackage{hyperref}

\begin{document}

	\input{intro.tex}

	\printbibliography

\end{document}